### 2014-09-23 generic.Rmd
RMarkdown now has residual tables.

```{r}
source("context-inference-fns.R")
cat(model@invocation)
```

@@

```{r}
computeresids(model)
```

>>>>

```{r}
library(pander)
panderOptions("table.split.table", Inf)  # Let tables become arbitrarily wide rather than wrapping.
source("context-inference-fns.R")
cat(model@invocation)
```

@@

```{r, results="asis"}
resids = computeresids(model)
pandoc.table(resids, style="rmarkdown")
```
